Fast gravitational wave parameter estimation without compromises

### 2023-07-25 src/tex/ms.tex
Slight update to the paragraph

%Structure of paper
The rest of the paper is structured as follows: we review the basics of PE and
introduce our framework in Sec.~\ref{sec: PE}; we present benchmarking results
on both simulated and real data in Sec.~\ref{sec: Result}; and, finally, we
discuss the implications of this work and directions for future development in
Sec.~\ref{sec: Discussion}. \corr{This study was carried out using the reproducibility
software showyourwork (Luger et al. 2021), which leverages continuous
integration to programmatically create the figures, and compile the
manuscript.The Git repository associated to this study is publicly available at
https://github.com/kazewong/TurboPE, and the release v2.1 allows anyone to
rebuild the entire manuscript. The repository is mirrored and stored at
10.5281/zenodo.8184855, including the data and the scripts used to produce the
figures. The version of \textsc{flowMC} used to produce this work is also stored
on zenodo at 10.5281/zenodo.7706605}

>>>>

%Structure of paper
The rest of the paper is structured as follows: we review the basics of PE and
introduce our framework in Sec.~\ref{sec: PE}; we present benchmarking results
on both simulated and real data in Sec.~\ref{sec: Result}; and, finally, we
discuss the implications of this work and directions for future development in
Sec.~\ref{sec: Discussion}. \corr{This study was carried out using the
reproducibility software showyourwork (Luger et al. 2021), which leverages
continuous integration to programmatically download the data from
https://zenodo.org, create the figures, and compile the manuscript. Each figure
caption contains two links: one to the data set stored on Zenodo used in the
corresponding figure, and the other to the script used to make the figure (at
the commit corresponding to the current build of the manuscript). The Git
repository associated to this study is publicly available at
https://github.com/kazewong/TurboPE, and the release v2.1 allows anyone to
rebuild the entire manuscript. The repository is mirrored and stored at
10.5281/zenodo.8184855, including the data and the scripts used to produce the
figures. The version of \textsc{flowMC} used to produce this work is also stored
on zenodo at 10.5281/zenodo.7706605}
